Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

Next, we will prove 
\begin{center}
    {\bf Claim 1:} If a segment $h \in \cross_H(r^*)$, then $h \in \dcross_H(\bm{t})$.
\end{center}
To prove the claim, we must show $h \in \dcross_H(\bm{t})$, or in other words, $h$ crosses both $\gbot(\bm{t}) = r'$ and $B_\bm{t}$.
\myitems {
    \item First, we explain why $h$ crosses $r'$. Because $r^* \subseteq r'$, the fact of $h$ crossing $r^*$ tells us that $h \cap r' \ne \emptyset$. On the other hand, the fact of $h$ crossing $r^*$ also tells us that $\xleft(h) < x_1 \le x_2 < \xright(h)$ (recall that $[x_1, x_2]$ is the x-range of $r^*$). As $[x_1, x_2]$ is also the x-range of $r'$, the fact of $h \cap r' \ne \emptyset$ indicates that $h$ must cross $r'$.

@@

Firstly, we will prove $\dcross_H(\bm{t})\subseteq \cross_H(r^*)$. For this purpose, given any segment $h \in \dcross_H(\bm{t})$, we will show that $h$ crosses $r^*$. To do so, we need to explain why $\xleft(h) < x_1 \le x_2 < \xright(h)$ and $y_h \in [y_1, \maxtop(r')]$.
\begin{itemize}
    \item The fact $h \in \dcross_H(\bm{t})$ tells us that $h$ crosses $\gbot(\bm{t})$, which is $r'$. As the x-range of $r'$ is $[x_1,x_2]$, it must hold true that $\xleft(h) < x_1 \le x_2 < \xright(h)$.

@@

    \item The fact $h \in \dcross_H(\bm{t})$ also tells us that $h$ crosses $B_{\bm{t}}$. Hence, $y_h \in [\ybot(B_\bm{t}), \ytop(B_{\bm{t}})]$. From $r' = \gbot(\bm{t})$, we get $\ybot(B_\bm{t}) = \ybot(r') = y_1$. By the definition of $\maxtop(r')$ in \eqref{eqn:hv:type1:maxtop}, we know $\ytop(B_{\bm{t}}) \leq \maxtop(r')$. It thus follows that $y_h \in [y_1, \maxtop(r')]$.
\end{itemize}
We can now conclude that $h$ crosses $r^*$.

@@

Secondly, assuming that the segments of $\cross_H(r^*)$ are sorted in ascending order of their y-coordinates,
we will prove that $\dcross_H(\bm{t})$ includes a prefix of the sorted order. It suffices to establish the following equivalent statement:

\minipg{0.8\linewidth} {
    If a segment $h \in \cross_H(r^*)$ has y-coordinate $y_h \le \ytop(B_{\bm{t}})$, then $h$ must be in $\dcross_H(\bm{t})$.
}

@@

@@

We first show that $h$ crosses $r'$, or equivalently: $\xleft(h)  < x_1 \leq x_2 < \xright(h)$ and $y_h \in [y_1, y_2]$. These conditions hold true because $h$ crosses $r^* = [x_1,x_2]\times [y_1, \maxtop(r')]$, and $\maxtop(r')\leq y_2$ (due to the definition of top-sliced rectangle in \eqref{eqn:hv:type1:topsliced}).

@@

Finally, we show that $h$ crosses $B_{\bm{t}}$, or equivalently: $\xleft(h) < \xleft(B_{\bm{t}}) \le \xright(B_{\bm{t}}) < \xright(h)$ and $y_h \in [\ybot(B_\bm{t}), \ytop(B_{\bm{t}})] = [y_1, \ytop(B_{\bm{t}})]$.
\begin{itemize}
    \item The fact of $h$ crossing $r'$ tells us $\xleft(h) < x_1 \leq x_2 < \xright(h)$. As $r' = \gbot(B_{\bm{t}})$, the x-range of $B_{\bm{t}}$ must be contained in $[x_1,x_2]$. Therefore, $\xleft(h) < \xleft(B_{\bm{t}}) \le \xright(B_{\bm{t}}) < \xright(h)$.

@@

    \item The fact of $h$ crossing $r^*$ also tells us that $y_h \in [y_1, \maxtop(r')]$. Moreover, by the definition of $h$, we have $y_h \leq \ytop(B_{\bm{t}})$. It thus follows that $y_h \in [y_1, \ytop(B_{\bm{t}})]$.
\end{itemize}

>>>>

Next, we will prove 
\begin{center}
    {\bf Claim 1:} If a segment $h \in \cross_H(r^*)$, then $h \in \dcross_H(\bm{t})$.
\end{center}
In other words, we must show that $h$ crosses both $\gbot(\bm{t}) = r'$ and $B_\bm{t}$.
\myitems {
    \item First, we explain why $h$ crosses $r'$. Because $r^* \subseteq r'$, the fact of $h$ crossing $r^*$ tells us that $h \cap r' \ne \emptyset$. On the other hand, the fact of $h$ crossing $r^*$ also tells us that $\xleft(h) < x_1 \le x_2 < \xright(h)$ (recall that $[x_1, x_2]$ is the x-range of $r^*$). As $[x_1, x_2]$ is also the x-range of $r'$, the fact of $h \cap r' \ne \emptyset$ indicates that $h$ must cross $r'$.

@@

First, we will prove $\dcross_H(\bm{t})\subseteq \cross_H(r^*)$ or equivalently: if a segment $h \in \dcross_H(\bm{t})$, then $h$ crosses $r^*$. To do so, we need to explain why $\xleft(h) < x_1 \le x_2 < \xright(h)$ and $y_h \in [y_1,$ $\maxtop(r')]$.
\begin{itemize}
    \item The fact of $h \in \dcross_H(\bm{t})$ tells us that $h$ crosses $\gbot(\bm{t})$, which is $r'$. As the x-range of $r'$ is $[x_1,x_2]$, it must hold true that $\xleft(h) < x_1 \le x_2 < \xright(h)$.

@@

    \item The fact of $h \in \dcross_H(\bm{t})$ also tells us that $h$ crosses $B_{\bm{t}}$. Hence, $y_h \in [\ybot(B_\bm{t}), \ytop(B_{\bm{t}})]$. From $r' = \gbot(\bm{t})$, we get $\ybot(B_\bm{t}) = \ybot(r') = y_1$. By the definition of $\maxtop(r')$ in \eqref{eqn:hv:type1:maxtop}, we know $\ytop(B_{\bm{t}}) \leq \maxtop(r')$. It thus follows that $y_h \in [y_1, \maxtop(r')]$.
\end{itemize}

Second, assuming that the segments of $\cross_H(r^*)$ are sorted in ascending order of their y-coordinates,
we will prove that $\dcross_H(\bm{t})$ includes a prefix of the sorted order. It suffices to establish the following equivalent claim:

@@

\minipg{0.8\linewidth} {
    {\bf Claim 2:} If a segment $h \in \cross_H(r^*)$ has y-coordinate $y_h \le \ytop(B_{\bm{t}})$, then $h$ must be in $\dcross_H(\bm{t})$.
}

@@

\myitems{

\item We first show that $h$ crosses $r'$, or equivalently: $\xleft(h)  < x_1 \leq x_2 < \xright(h)$ and $y_h \in [y_1, y_2]$. These conditions hold true because $h$ crosses $r^* = [x_1,x_2]\times [y_1, \maxtop(r')]$, and $\maxtop(r')\leq y_2$ (due to the definition of a top-sliced rectangle in \eqref{eqn:hv:type1:topsliced}).

@@

\item Next we show that $h$ crosses $B_{\bm{t}}$, or equivalently: $\xleft(h) < \xleft(B_{\bm{t}}) \le \xright(B_{\bm{t}}) < \xright(h)$ and $y_h \in [\ybot(B_\bm{t}), \ytop(B_{\bm{t}})] = [y_1, \ytop(B_{\bm{t}})]$.

@@

\begin{itemize}
    \item The fact of $h$ crossing $r'$ tells us $\xleft(h) < x_1 \leq x_2 < \xright(h)$. As $r' = \gbot(B_{\bm{t}})$, the x-range of $B_{\bm{t}}$ must be contained in $[x_1,x_2]$. Thus, $\xleft(h) < \xleft(B_{\bm{t}}) \le \xright(B_{\bm{t}}) < \xright(h)$.

@@

    \item The fact of $h$ crossing $r^*$ also tells us that $y_h \in [y_1, \maxtop(r')]$. Moreover, Claim 2 explicitly gives us the condition $y_h \leq \ytop(B_{\bm{t}})$. It thus follows that $y_h \in [y_1, \ytop(B_{\bm{t}})]$.
\end{itemize}
}
